\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-11 paper/main.tex
Addressed some comments

\textbf{Handling bugs in specific GPU-CUDA versions requires OS
  changes:} Many of the GPU-related bugs can only be repro duced with
specific GPU builds\Fix{I don't understance GPU builds. do you mean
  GPU vendor/version? give example} and specific CUDA builds. Changing
different virtual environments does not change the CUDA
versions\Fix{Do you mean ``it is not possible to change the CUDA (or
  GPU) version with Python's virtual environments''?} of the
system. That is why we use Docker when a bug relies on a specific
version of CUDA to be installed in the system.

>>>>

\textbf{Handling bugs in specific GPU-CUDA versions requires OS
  changes:} Many of the GPU-related bugs can only be reproduced with
library versions that are built with specific versions of CUDA.
These builds require those specific CUDA drivers to be installed on
the system, and the version of the CUDA driver installed on a system
can not be changed with Python's virtual enviroments.
% GPU builds\Fix{I don't understance GPU builds. do you mean
%   GPU vendor/version? give example} and specific CUDA builds. 
% Changing different virtual environments does not change the CUDA
% versions\Fix{Do you mean ``it is not possible to change the CUDA (or
%   GPU) version with Python's virtual environments''?} of the
% system. 
% That is why we use Docker when a bug relies on a specific
% version of CUDA to be installed in the system.
That is why we use Docker Containers with specific CUDA drivers to reproduce
such bugs instead of virtual enviroments.
